Fixed-Parameter Tractable Sampling for RNA Design with Multiple Target Structures

### 2019-01-23 supplement.tex
fig change

\begin{figure}[tbh]
  \centering
  \includegraphics[width=0.45\textwidth]{Figs/RunTimes/construction_time_sets}\quad%
  \includegraphics[width=0.45\textwidth]{Figs/RunTimes/sample_time_sets}\\
  \includegraphics[width=0.45\textwidth]{Figs/RunTimes/construction_time_sets_bp}\quad%
  \includegraphics[width=0.45\textwidth]{Figs/RunTimes/sample_time_sets_bp}
  \caption{Boxplots showing the run-time distribution of sequence sampling with \ourprog{} for the various benchmark sets. The times are split into construction time (left) and sampling time (right). Construction includes all the pre-computation, while the latter is the time needed to generate 20.000 sequences. Furthermore, we distinguish between two energy models, stacking (top) and basepair (bottom). }
  \label{fig:run-times-redprint}
\end{figure}
\begin{figure}[tbh]
  \centering
  \includegraphics[width=0.45\textwidth]{Figs/RunTimes/construction_time_sets_rbp}\quad%
  \includegraphics[width=0.45\textwidth]{Figs/RunTimes/sample_time_sets_rbp}
  \caption{Boxplots showing the run-time distribution of sequence sampling with \RNAblueprint{} for the various benchmark sets. The times are split into construction time (left) and sampling time (right). Construction includes all the pre-computation, while the latter is the time needed to generate 20.000 sequences.}
  \label{fig:run-times-rbp}
\end{figure}

>>>>

\begin{figure}[tbh]
  \centering
  \includegraphics[width=0.45\textwidth]{Figs/RunTimes/construction_time_sets}\quad%
  \includegraphics[width=0.45\textwidth]{Figs/RunTimes/sample_time_sets}
  \caption{Boxplots showing the run-time distribution of sequence sampling with \ourprog{} for the various benchmark sets. The times are split into construction time (left) and sampling time (right). Construction includes all the pre-computation, while the latter is the time needed to generate 20.000 sequences. }
  \label{fig:run-times-redprint}
\end{figure}
\begin{figure}[tbh]
  \centering
  \includegraphics[width=0.45\textwidth]{Figs/RunTimes/construction_time_sets_rbp}\quad%
  \includegraphics[width=0.45\textwidth]{Figs/RunTimes/sample_time_sets_rbp}
  \caption{Boxplots showing the run-time distribution of sequence sampling with \RNAblueprint{} for the various benchmark sets. The times are split into construction time (left) and sampling time (right). Construction includes all the pre-computation, while the latter is the time needed to generate 20.000 sequences.}
  \label{fig:run-times-rbp}
\end{figure}
